%
% File naaclhlt2016.tex
%

\documentclass[11pt]{article}
\usepackage{style/naaclhlt2016}
\naaclfinalcopy
\def\naaclpaperid{234}

\usepackage{times}
\usepackage{url}
\usepackage{setspace}
\usepackage{latexsym}
\usepackage{CJKutf8}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\usepackage{ulem}
\usepackage{courier}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage[T1]{fontenc}
\normalem

\newcommand{\todo}[1]{({\bf TODO:} #1)}
\newcommand{\trans}{{Translationese}}
\newcommand{\inter}{{Interpretese}}
\newcommand{\jatext}[1]{\begin{CJK}{UTF8}{min}#1\end{CJK}}
\newcommand{\pos}[1]{{\small \texttt{#1}}}
\renewcommand{\S}{$\langle$S$\rangle$}
\renewcommand{\SS}{$\langle$SS$\rangle$}
\newcommand{\E}{$\langle$E$\rangle$}
\newcommand{\EE}{$\langle$EE$\rangle$}


\definecolor{darkblue}{rgb}{0.0,0.0,0.5}
\definecolor{darkpurple}{rgb}{0.4,0.0,0.4}
\definecolor{darkred}{rgb}{0.5,0.0,0.0}
\definecolor{darkgreen}{rgb}{0.0,0.5,0.0}

\newcommand{\summarized}[1]{\textcolor{darkred}{\uwave{#1}}}
\newcommand{\moregeneral}[1]{\emph{\textcolor{darkpurple}{#1}}}
\newcommand{\Segment}{\textcolor{darkgreen}{\langle\big\|\rangle}}
\newcommand{\passivized}[1]{\textcolor{darkblue}{\underline{#1}}}

\newcommand{\Gn}{\moregeneral{generalize}}
\newcommand{\Sg}{segment $\Segment$}
\newcommand{\Sm}{\summarized{summarize}}
\newcommand{\Ps}{\passivized{passivize}}
\newcommand{\Om}{(omit)}
\newcommand{\Source}[1]{{(S)\hspace{1ex}\jatext{#1}}}
\newcommand{\Trans}[1]{{(T)\hspace{1ex}#1}}
\newcommand{\Inter}[1]{{(I)\hspace{1ex}#1}}

\makeatletter
\newcommand{\@BIBLABEL}{\@emptybiblabel}
\newcommand{\@emptybiblabel}[1]{}
\makeatother
\usepackage{hyperref}

\naaclfinalcopy % Uncomment this line for the final submission

% To expand the titlebox for more authors, uncomment
% below and set accordingly.
% \addtolength\titlebox{.5in}

\frenchspacing
\newif\ifcomment\commentfalse

\input{style/preamble}

\title{Interpretese vs. Translationese: \\ The Uniqueness of Human Strategies in Simultaneous Interpretation}

\author{He He \\
  Computer Science \\
  University of Maryland \\
  {\tt hhe@cs.umd.edu} \\\And
  Jordan Boyd-Graber \\
  Computer Science \\
  University of Colorado \\
{\tt Jordan.Boyd.Graber} \\
   {\tt @colorado.edu} \\ \And
  Hal {Daum\'e III} \\
  Computer Science and \abr{umiacs} \\
  University of Maryland \\
  {\tt hal@cs.umd.edu}}

\date{}

\begin{document}
\maketitle
\begin{abstract}
  Computational approaches to simultaneous interpretation are stymied
  by how little we know about the tactics human interpreters use. We
  produce a parallel corpus of translated and simultaneously
  interpreted text and study differences between them through a
  computational approach.  Our analysis reveals that human
  interpreters regularly apply several effective tactics to reduce
  translation latency, including sentence segmentation and
  passivization.  In addition to these unique, clever strategies, we
  show that limited human memory also causes other idiosyncratic
  properties of human interpretation such as generalization and
  omission of source content.
\end{abstract}

\input{2016_naacl_interpretese/sections/introduction}
\input{2016_naacl_interpretese/sections/classification}
\input{2016_naacl_interpretese/sections/experiments}
\input{2016_naacl_interpretese/sections/conclusion}
\input{2016_naacl_interpretese/sections/features}

\section*{Acknowledgments}

We thank CIAIR (Nagoya University, Japan) for providing the interpretation data which
formed the foundation of this research.
We also thank Alvin Grissom~II, Naho Orita and the reviewers for their insightful comments.
This work was supported by
\abr{nsf} grant \abr{iis}-1320538.  Boyd-Graber is also partially
supported by \abr{nsf} grants \abr{ccf}-1409287 and
\abr{ncse}-1422492. Any opinions, findings,
conclusions, or recommendations expressed here are those of the
authors and do not necessarily reflect the view of the sponsor.

%\clearpage

\bibliographystyle{style/naaclhlt2016}
\bibliography{bib/journal-full,bib/jbg,bib/hhe}

\end{document}
