\subsubsection{\triviaqa{} multi-answer examples:}
\label{appendix:trivia-qa-examples}
\small{We randomly sample 100 examples from \triviaqa{} where questions had multiple answers.}
\\ 
\setlength{\parindent}{0cm}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{sfq\_6110}} \\
Q: \textit{On which island in the North Sea did both St Aidan and St Cuthbert live?} \\
A: \entity{Lindisfarne } \\
A: \entity{LINDISFARNE}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{tc\_1008}} \\
Q: \textit{To the nearest two, how many tennis Grand Slam titles did Jimmy Connors win?} \\
A: \entity{10} \\
A: \entity{ten}}


\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{sfq\_26211}} \\
Q: \textit{In the TV series Doctor Who, who was the creator of the Daleks and arch enemy of the Doctor?} \\
A: \entity{Davros} \\
A: \entity{Creator of the Daleks}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{sfq\_22212}} \\
Q: \textit{In which book of the bible is the story of Samson and Delilah?} \\
A: \entity{Judge (disambiguation)} \\
A: \entity{Judges}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{bt\_1538}} \\
Q: \textit{What is cartoon character Mr. Magoo's first name} \\
A: \entity{Quincy (disambiguation)} \\
A: \entity{Quincy}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{qz\_2444}} \\
Q: \textit{What is Robin Williams character called in Good Morning Vietnam?} \\
A: \entity{Adrian}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{sfq\_22693}} \\
Q: \textit{What was the first name of the jazz trombonist Kid Ory?} \\
A: \entity{Eadweard} \\
A: \entity{Edward}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{qw\_1606}} \\
Q: \textit{Which of Queen Elizabeth's children is the lowest in succession to (i.e. furthest away from) the throne?} \\
A: \entity{Anne} \\
A: \entity{Ann (name)}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{odql\_5503}} \\
Q: \textit{"Which radio comedian's catchphrase was ""daft as a brush""?"} \\
A: \entity{KEN PLATT} \\
A: \entity{Ken Platt}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{qg\_2992}} \\
Q: \textit{According to Sammy Haggar, what can't he drive?} \\
A: \entity{55} \\
A: \entity{fifty-five}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{qf\_3440}} \\
Q: \textit{What was Grace Darling's father's job?} \\
A: \entity{Lighthouse-keeper} \\
A: \entity{Lighthouse keeper}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{qw\_12369}} \\
Q: \textit{"What year did Jean-Francois Champollion publish the first correct translation of Egyptian hieroglyphs from the Rosetta Stone, the Roman Catholic Church take Galileo Galilei's ""Dialogue"" off their list of banned books, and Britain repeal the death penalty for over 100 crimes?"} \\
A: \entity{one thousand, eight hundred and twenty-two} \\
A: \entity{1822}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{qw\_4143}} \\
Q: \textit{What is the title of the most famous painting by Franz Hals?} \\
A: \entity{Laughing Cavalier} \\
A: \entity{The Laughing Cavalier}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{qb\_2647}} \\
Q: \textit{What is the title of the 1944 film starring Barbara Stanwyck as the wife who seduces an insurance salesman into killing her husband?} \\
A: \entity{Double indemnity (disambiguation)} \\
A: \entity{Double Indemnity}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{sfq\_22920}} \\
Q: \textit{Who was the choreographer of the dance troupe Hot Gossip?} \\
A: \entity{Arlene Philips} \\
A: \entity{Arlene Phillips}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{tc\_719}} \\
Q: \textit{River Phoenix died during the making of which movie?} \\
A: \entity{Dark Blood (film)} \\
A: \entity{Dark Blood}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{sfq\_19457}} \\
Q: \textit{Who won the first ever boxing gold for women? She shares her surname with two US Presidents.} \\
A: \entity{Nicola Adams} \\
A: \entity{Adams, Nicola}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{sfq\_8996}} \\
Q: \textit{Actor Norman Painting died in November 2009, which part in a log running radio series did he make his own?} \\
A: \entity{PHIL ARCHER} \\
A: \entity{Phil Archer}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{dpql\_6111}} \\
Q: \textit{Which Jersey-born actor played Superman in Man of Steel?} \\
A: \entity{Henry Cavill} \\
A: \entity{Henry William Dalgliesh Cavill}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{qz\_2135}} \\
Q: \textit{Name the game show, presented by Leslie Grantham and Melinda Messenger, where contestants were set physical and mental challenges?} \\
A: \entity{Fort Boyard (disambiguation)} \\
A: \entity{Fort Boyard}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{odql\_3205}} \\
Q: \textit{Who wrote the novel 'The Beach' on which the film was based?} \\
A: \entity{Alex Garland} \\
A: \entity{ALEX GARLAND}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{qz\_2999}} \\
Q: \textit{In what year did Edward Vlll abdicate?} \\
A: \entity{one thousand, nine hundred and thirty-six} \\
A: \entity{1936}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{tc\_723}} \\
Q: \textit{Which artist David was born in Bradford UK?} \\
A: \entity{Hockney} \\
A: \entity{David Hockney}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{odql\_3708}} \\
Q: \textit{Three Liverpool players were in the 1966 England World Cup winning squad. Roger Hunt and Ian Callaghan were two – who was the third?} \\
A: \entity{Gerry Byrne} \\
A: \entity{Gerry Byrne (disambiguation)}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{qw\_11151}} \\
Q: \textit{Which artist has a daughter and two sons with Jane Asher, whom he married in 1981?} \\
A: \entity{Gerald Anthony Scarfe} \\
A: \entity{Gerald Scarfe}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{qb\_3652}} \\
Q: \textit{Who wrote the novel ‘The Eagle Has landed’?} \\
A: \entity{Harry Patterson} \\
A: \entity{Jack Higgins}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{odql\_14683}} \\
Q: \textit{Who presents the BBC quiz show ‘Perfection’?} \\
A: \entity{Nick Knowles} \\
A: \entity{NICK KNOWLES}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{sfq\_9464}} \\
Q: \textit{Who succeeded Brian Epstein as manager of The Beatles?} \\
A: \entity{Allan Klein} \\
A: \entity{Allen Klein}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{wh\_2615}} \\
Q: \textit{In which year did both T-Rex's Marc Bolan and Elvis Presley die ?} \\
A: \entity{1977} \\
A: \entity{one thousand, nine hundred and seventy-seven}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{sfq\_9018}} \\
Q: \textit{Who played Hotlips Houlihan in the 1972 film MASH?} \\
A: \entity{Sally Kellerman} \\
A: \entity{SALLY KELLERMAN}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{qz\_1516}} \\
Q: \textit{Who bought Chelsea football club for £1 in 1982?} \\
A: \entity{Ken Bates} \\
A: \entity{Kenneth Bates}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{sfq\_23289}} \\
Q: \textit{What was the middle name of the author William Thackeray?} \\
A: \entity{Makepeace} \\
A: \entity{MAKEPEACE}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{sfq\_7589}} \\
Q: \textit{What was the name of the older brother of Henry 8th?} \\
A: \entity{Arthur} \\
A: \entity{Arthur (name)}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{odql\_10316}} \\
Q: \textit{Which actor played 'Hadley', in the TV series of the same name?} \\
A: \entity{GERALD HARPER} \\
A: \entity{Gerald Harper}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{sfq\_12933}} \\
Q: \textit{Operation Barbarossa, Hitler invades Russia.} \\
A: \entity{one thousand, nine hundred and forty-one} \\
A: \entity{1941}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{qw\_5050}} \\
Q: \textit{"Which Italian nobel prize winner (1934) wrote novels such as ""Mal Gioconda"" and switched to writing plays in 1910?"} \\
A: \entity{Pirandello} \\
A: \entity{Luigi Pirandello}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{bt\_2403}} \\
Q: \textit{What was the name of the driver of the mail train robbed by the great train robbers} \\
A: \entity{Jack Mills (train driver)} \\
A: \entity{Jack Mills}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{sfq\_2189}} \\
Q: \textit{What was the name of the private eye played by Trevor Eve on TV in the '70s?} \\
A: \entity{Shoestring (TV series)} \\
A: \entity{Eddie Shoestring}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{qb\_5431}} \\
Q: \textit{Brazilian football legend Pele wore which number on his shirt?} \\
A: \entity{10} \\
A: \entity{ten}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{qb\_4726}} \\
Q: \textit{Michael J Fox travels back to which year in the Wild West in the 1990 film ‘Back To The Future Part III’?} \\
A: \entity{one thousand, eight hundred and eighty-five} \\
A: \entity{1885}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{odql\_8275}} \\
Q: \textit{Later a 'Blue Peter' presenter, who played 'Steven Taylor', an assistant to William Hartnell's 'Doctor Who'?} \\
A: \entity{PETER PURVES} \\
A: \entity{Peter Purves}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{sfq\_962}} \\
Q: \textit{Which city was the subject of the 1949 song 'Dirty Old Town' by Ewan McColl?} \\
A: \entity{Salford} \\
A: \entity{Salford (disambiguation)}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{tc\_1348}} \\
Q: \textit{In the late 60s Owen Finlay MacLaren pioneered what useful item for parents of small chldren?} \\
A: \entity{Baby Buggy} \\
A: \entity{Baby buggy}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{qw\_12732}} \\
Q: \textit{General Franco, the Spanish military general, was head of state of Spain from October 1936 following the Spanish Civil War, until when?} \\
A: \entity{1975} \\
A: \entity{one thousand, nine hundred and seventy-five}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{bt\_4495}} \\
Q: \textit{Which of the Great Train Robbers became a florist outside Waterloo station until he was found hanged in a lock up} \\
A: \entity{Buster Edwards} \\
A: \entity{Ronald \%22Buster\%22 Edwards}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{sfq\_20394}} \\
Q: \textit{Which TV presenter, who died in February 2013, was for over 20 years the host of 'Mr \& Mrs'?} \\
A: \entity{Derek Batey} \\
A: \entity{Derek Beatty}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{odql\_12918}} \\
Q: \textit{Which British political party leader is MP for Westmorland and Lonsdale?} \\
A: \entity{Tim Farron} \\
A: \entity{Timothy Farron}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{odql\_13785}} \\
Q: \textit{Who wrote the lyrics for 'Sing', written to celebrate the Queen's Diamond Jubilee?} \\
A: \entity{Gary Barlow} \\
A: \entity{GARY BARLOW}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{sfq\_20830}} \\
Q: \textit{Which top National Hunt trainer's establishment is based at Seven Barrows?} \\
A: \entity{NICKY HENDERSON} \\
A: \entity{Nicky Henderson}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{wh\_2133}} \\
Q: \textit{Which T.V. Quiz show host used the catchphrase :- If its' up there, I'll give you the money myself ?} \\
A: \entity{LES DENNIS} \\
A: \entity{Les Dennis}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{sfq\_15663}} \\
Q: \textit{The 27 episodes of which sitcom featuring Julia Mckenzie, Anton Rodgers and Ballard Berkley were first broadcast in the 1980s?} \\
A: \entity{Fresh Fields (TV series)} \\
A: \entity{Fresh Fields}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{odql\_4871}} \\
Q: \textit{When US President James Garfield was shot in Washington DC in July 1881, what was he doing?} \\
A: \entity{WAITING FOR A TRAIN} \\
A: \entity{Waiting for a Train}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{bb\_6592}} \\
Q: \textit{Which artist was born in Bradford in 1937?} \\
A: \entity{Hockney} \\
A: \entity{David Hockney}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{qw\_10270}} \\
Q: \textit{Argentina invaded UK's Falkland Islands, Israel invaded Southern Lebanon, Canada became officially independent of the UK, Leonid Brezhnev, leader of the USSR, died, all in what year?} \\
A: \entity{one thousand, nine hundred and eighty-two} \\
A: \entity{1982}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{bt\_4206}} \\
Q: \textit{Who was the first woman to be seen on Channel 4} \\
A: \entity{Carol Vorderman} \\
A: \entity{Carol Voderman}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{qw\_8871}} \\
Q: \textit{Lieutenant General James Thomas Brudenell, who commanded the Light Brigade of the British Army during the Crimean War, was the 7th Earl of what?} \\
A: \entity{Cardigan} \\
A: \entity{Cardigan (disambiguation)}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{sfq\_13639}} \\
Q: \textit{Which model village did Samuel Greg build to house workers at his nearby Quarry Bank Mill?} \\
A: \entity{Styal} \\
A: \entity{STYAL}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{tc\_812}} \\
Q: \textit{Who was the defending champion when Martina Navratilova first won Wimbledon singles?} \\
A: \entity{Virginia Wade} \\
A: \entity{Sarah Virginia Wade}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{sfq\_11790}} \\
Q: \textit{Opened in 1963, which London nightclub did Mark Birley name after his then wife?} \\
A: \entity{Annabel's} \\
A: \entity{ANNABELS}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{qw\_8397}} \\
Q: \textit{In 1995, Steffi Graf became the only tennis player to have won each of the four grand slam events how many times?} \\
A: \entity{four} \\
A: \entity{4}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{dpql\_3151}} \\
Q: \textit{On which river does Ipswich stand?} \\
A: \entity{Orwell (disambiguation)} \\
A: \entity{Orwell}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{qw\_14634}} \\
Q: \textit{"Which Bob Dylan song begins ""You got a lotta nerveTo say you are my friend. When I was down, You just stood there grinning""?"} \\
A: \entity{Positively Fourth Street} \\
A: \entity{Positively 4th Street}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{dpql\_1801}} \\
Q: \textit{Nick Begs was lead singer with which 80’s pop band?} \\
A: \entity{Kaja Googoo} \\
A: \entity{Kajagoogoo}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{qw\_16011}} \\
Q: \textit{In 1483, who was appointed the first grand inquisitor of the Spanish Inquisition?} \\
A: \entity{Torquemada (disambiguation)} \\
A: \entity{Torquemada}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{qw\_1933}} \\
Q: \textit{What remake of a British science-fiction serial broadcast by BBC Television in the summer of 1953 was staged live by BBC Four in 2005 with actors Jason Flemyng, Mark Gatiss, Andrew Tiernan, Indira Varma, David Tennant and Adrian Bower?} \\
A: \entity{Quatermass experiment} \\
A: \entity{The Quatermass Experiment}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{odql\_2323}} \\
Q: \textit{Which 2009 film is a biopic of John Lennon?} \\
A: \entity{'NOWHERE BOY'} \\
A: \entity{Nowhere Boy}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{bb\_522}} \\
Q: \textit{'The Battle of Trafalgar' is the work of which British painter?} \\
A: \entity{Joseph Turner} \\
A: \entity{Joseph Turner (disambiguation)}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{qw\_4463}} \\
Q: \textit{Who discovered the two moons of Mars in 1877?} \\
A: \entity{Asaph Hall} \\
A: \entity{Asaph Hall III}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{qz\_1111}} \\
Q: \textit{Which brand of beer does Homer Simpson drink regularly?} \\
A: \entity{Duff} \\
A: \entity{Duff (disambiguation)}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{wh\_8}} \\
Q: \textit{In the novel 'Treasure Island' name the pirate shot dead by Jim Hawkins in the rigging of the Hispaniola} \\
A: \entity{Israel Hands} \\
A: \entity{ISRAEL HANDS}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{qg\_3884}} \\
Q: \textit{Dow Constantine and Susan Hutchinson are currently running for was position?} \\
A: \entity{King County executive} \\
A: \entity{King County Executive}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{sfq\_25940}} \\
Q: \textit{Which actor played the part of Ross Poldark in the BBC’s mid 1970’s television series?} \\
A: \entity{Robin Ellis} \\
A: \entity{ROBIN ELLIS}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{odql\_12777}} \\
Q: \textit{For which 1960 film did Billy Wilder become the first person to win three Oscars for the same film?} \\
A: \entity{The Apartment} \\
A: \entity{The apartment}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{bb\_4540}} \\
Q: \textit{Famous for 'Die Welt als Wille und Vorstellung', Arthur Schopenhauer (1788-1860) was a German?} \\
A: \entity{Philosophers} \\
A: \entity{Philosopher}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{qb\_8589}} \\
Q: \textit{What is the nickname of the frontiersman Nathaniel Poe, played by Daniel Day Lewis, in the 1992, film ‘The Last of the Mohicans’?} \\
A: \entity{Hawkeye} \\
A: \entity{Hawkeye (disambiguation)}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{bt\_2852}} \\
Q: \textit{Who played the part of Tina Seabrook in Casualty} \\
A: \entity{Claire Woodrow} \\
A: \entity{Claire Goose}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{wh\_557}} \\
Q: \textit{Who duetted with Syd Owen on the single Better Believe It, which was released as part of the Children in Need appeal in 1995 ?} \\
A: \entity{PATSY PALMER} \\
A: \entity{Patsy Palmer}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{odql\_3979}} \\
Q: \textit{What is the name of the character played by Nicole Kidman in the film 'Moulin Rouge'?} \\
A: \entity{Satine} \\
A: \entity{'SATINE'}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{odql\_10365}} \\
Q: \textit{Which British girl won the Women's Junior Singles title at Wimbledon this year (2008)?} \\
A: \entity{LAURA ROBSON} \\
A: \entity{Laura Robson}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{qf\_1735}} \\
Q: \textit{In what year did Elvis Presley and his parents move from Tupelo to Memphis?} \\
A: \entity{one thousand, nine hundred and forty-eight} \\
A: \entity{1948}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{tc\_1468}} \\
Q: \textit{What was Pete Sampras seeded when he won his first US Open?} \\
A: \entity{twelve} \\
A: \entity{12}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{qf\_2679}} \\
Q: \textit{Who on TV has played a scarecrow and a Time Lord?} \\
A: \entity{John Pertwee} \\
A: \entity{Jon Pertwee}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{sfq\_11844}} \\
Q: \textit{In which year was Olaf Palme assassinated and the Chernobyl nuclear power station exploded?} \\
A: \entity{1986} \\
A: \entity{one thousand, nine hundred and eighty-six}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{qf\_3578}} \\
Q: \textit{Cassandra was the pseudonym of which writer in the Daily Mirror?} \\
A: \entity{William Neil Connor} \\
A: \entity{William Connor}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{qz\_3898}} \\
Q: \textit{How many times did Steffi Graf win the Ladies Singles at Wimbledon?} \\
A: \entity{seven} \\
A: \entity{7}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{qw\_6782}} \\
Q: \textit{What is the disease that Stephen Hawking has?} \\
A: \entity{Motor neuron disease} \\
A: \entity{Motor neuron diseases}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{qw\_15255}} \\
Q: \textit{"How many films were made by director Sir Peter Jackson from Tolkien's short book, ""The Hobbit""?"} \\
A: \entity{3} \\
A: \entity{three}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{sfq\_7168}} \\
Q: \textit{Who invented the wind-up radio?} \\
A: \entity{Trevor Bayliss} \\
A: \entity{TREVOR BAYLISS}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{sfq\_14433}} \\
Q: \textit{In Pride and Prejudice what was the first name of Mr Darcy?} \\
A: \entity{Fitzwilliam (disambiguation)} \\
A: \entity{Fitzwilliam}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{odql\_8230}} \\
Q: \textit{Which single by 'Leapy Lee' reached number two in the UK charts in 1968?} \\
A: \entity{'LITTLE ARROWS'} \\
A: \entity{Little Arrows}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{dpql\_1416}} \\
Q: \textit{Whose is the first tale in Chaucer’s Canterbury Tales?} \\
A: \entity{The Knight} \\
A: \entity{Knight (disambiguation)}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{qw\_1672}} \\
Q: \textit{Which womens squash player won the World Open four times (1985, 1987, 1990 \& 1992) and the British Open eight times?} \\
A: \entity{Susan Devoy} \\
A: \entity{Susan Elizabeth Anne Devoy}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{qz\_832}} \\
Q: \textit{Who wrote the novels About A Boy, How To Be Good and High Fidelity?} \\
A: \entity{Nick Hornby} \\
A: \entity{Hornby, Nick}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{sfq\_22884}} \\
Q: \textit{Which TV series was about a pop group called 'Little Ladies' featuring Charlotte Cornwell, Julie Covington and Rula Lenska?} \\
A: \entity{Rock Follies} \\
A: \entity{Rock Follies of '77}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{odql\_10746}} \\
Q: \textit{Who wrote the 1951 novel ‘The Caine Mutiny’?} \\
A: \entity{HERMAN WOUK} \\
A: \entity{Herman Wouk}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{bb\_285}} \\
Q: \textit{Said to refer erroneously to the temperature at which book paper catches fire, the title of Ray Bradbury's 1953 novel about a futuristic society in which reading books is illegal, is called 'Fahrenheit...' what? 972; 451; 100; or 25?} \\
A: \entity{451} \\
A: \entity{four hundred and fifty-one}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{odql\_7290}} \\
Q: \textit{Who was the driver of the limousine at the time of Diana Princess of Wales' death?} \\
A: \entity{HENRI PAUL} \\
A: \entity{Henri Paul}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{sfq\_4368}} \\
Q: \textit{Which island in the Grenadines of St. Vincent was bought by Colin Tennant in 1958? Princess Margaret built a holiday home there in the 1960's.} \\
A: \entity{MUSTIQUE} \\
A: \entity{Mustique}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{odql\_5476}} \\
Q: \textit{Which pop star had the real name of Ernest Evans?} \\
A: \entity{Chubby Checker} \\
A: \entity{'CHUBBY CHECKER'}}

\tiny{\setlength{\parindent}{0cm}
\textbf{id: \texttt{tc\_980}} \\
Q: \textit{"Which supermodel said, ""I look very scary in the mornings?"} \\
A: \entity{We don't wake up for less than \$10,000 a day} \\
A: \entity{Linda Evangelista}}
