\section{A Dataset of Character Interactions}
\label{sec:data}

Our dataset consists of 1,383 fictional works pulled from Project
Gutenberg and other Internet sources. Project Gutenberg has a limited
selection (outside of science fiction) of mostly classic literature,
so we add more contemporary novels from various genres such as
mystery, romance, and fantasy to our dataset.

To identify character mentions, we run the Book-\abr{nlp} pipeline of
\newcite{bamman-underwood-smith:2014:P14-1}, which includes character name
clustering, quoted speaker identification, and coreference
resolution.\footnote{While this pipeline works reasonably well, it is unreliable
  for first-person narratives; we leave the necessary improvements to character
  name clustering, which are further expanded upon in \newcite{vala2015mr}, for
  future work.} For every detected character mention, we define a span as
beginning 100 tokens before the mention and ending 100 tokens after the
mention. We do not use sentence or paragraph boundaries because they vary
considerably depending on the author (e.g., William Faulkner routinely wrote
single sentences longer than many of Hemingway's paragraphs). All spans in our
dataset contain mentions to exactly two characters. This is a rather strict
requirement that forces a reduction in data size, but spans in which more than
two characters are mentioned are generally noisier.

Once we have identified usable spans in the dataset, we apply a second filtering
step that removes relationships containing fewer than five spans. Without this
filter, our dataset is dominated by fleeting interactions between minor
characters; this is undesirable since our focus is on longer, mutable
relationships. Finally, we filter our vocabulary by removing the 500 most
frequently occurring words, as well as all words that occur in fewer than 100
books. The latter step helps correct for variation in time period and genre
(e.g., ``thou'' and ``thy'' found in older works like the \textit{Canterbury
  Tales}). Our final dataset contains 20,013 relationships and 380,408 spans,
while our vocabulary contains 16,223 words.\footnote{Code and span data
  available at \url{http://github.com/miyyer/rmn}.}
