\section*{Ethical Considerations}
 \label{sec:ethics}
Releasing a large dataset that can potentially be used to produce offensive content is not a decision we take lightly. We review relevant responsible disclosure information \cite{kirichenko2020best, cencini2005software} and determine that this dataset is safe to release for multiple reasons. Considering the widespread availability of robust jailbreaks online\footnote{https://www.jailbreakchat.com}, we believe that this resource holds more value for defensive applications than for offensive purposes. Before initiating the competition, we informed our sponsors of our intention to release the data as open source. We feel comfortable doing so without a special company access period for the following reasons:
\begin{enumerate}
    \item The existence of jailbreaks: As mentioned earlier, there are numerous jailbreaks readily available online. Our dataset does not introduce any significant new vulnerabilities that are not already accessible to those who seek them.
    \item No increased harm: Our dataset does not contain any harmful content that could be used to cause damage. Instead, it serves as a resource for understanding and mitigating potential risks associated with language models.
    \item Raising awareness: By releasing this dataset, we aim to call attention to the potential risks and challenges associated with large language models. This will encourage researchers and developers to work on improving the safety and security of these models.
    \item Encouraging responsible use: Companies should be cautious when using large language models in certain applications. By making this dataset available, we hope to encourage responsible use and development of these models.

\end{enumerate}