\section{More Examples}
 \color{red} [TODO: Temp section with more examples in cases we
 needed any of them.]\color{black}
 
\subsection*{Example 1}
Leadin: The title goddess huddles on a red cloth next to a shivering Cupid in this artist's Venus Frigida. For 10 points each:

[10] Name this painter of a self-portrait with his first wife called The Honeysuckle Bower. This artist of a Descent from the Cross and the Marie de' Medici cycle is noted for his depictions of voluptuous women.

ANSWER: Peter Paul Rubens

[10] Rubens' first wife was this woman, who is also the subject of a portrait by Anthony van Dyck.

ANSWER: Isabella Brant

[10] Rubens collaborated with the elder of the two painters named Jan from this family. Another member of this family painted The Fight Between Carnival and Lent and The Tower of Babel.

ANSWER: Brueghel


\subsection*{Example 2}
Question: This character is always praised at the end of the Two Minutes Hate. For 10 points each:

[10] Name this character who is "always watching you" and is opposed by Emmanuel Goldstein. This enigmatic dictator is often used as a symbol for excessive or abusive government power.

ANSWER: Big Brother

[10] Big Brother appears in this novel about Winston Smith by George Orwell, which details the dystopian society of Oceania ruled by the Party. Winston falls in love with Julia and is later tortured by O'Brien.

ANSWER: Nineteen Eighty-Four

[10] George Orwell coined this term, similar to cognitive dissonance, in Nineteen Eighty-Four. It describes the simultaneous acceptance of two contradictory beliefs.

ANSWER: doublethink
